### 2013-02-15 doc/icml2013/evaluation.tex
Now featuring more graphs

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
    \hspace{-2em}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\todo{Dataset 2}: $b = 30$, $p = 1$ [TODO]

\paragraph{Motion tracking data?}

@@

Using canonical settings, on the various datasets

Plot the parameters: the curves, three algorithms (DONE)

Plot: the histogram over errors (for EM?)

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\textwidth]{figures/vs-n/1-8-3-3.pdf}
  \caption{}
  \label{fig:vs-n}
\end{figure}

>>>>

\begin{figure*}[t]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between SpectralExperts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. Whilst
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\todo{Dataset 2: $b = 30$, $p = 1$. I'm unclear as to what we can show
on this sort of data set. EM works extremely well, and the spectral
methods do not converge easily.}

@@

Using canonical settings, on the various datasets: \tableref{tbl:parameter-recovery}.

Plot: the histogram over errors (for EM?) \todo{Some plots I have doesn't really show much}.

@@

\begin{figure*}[t]
  \centering
  \subfigure[Complete Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3.pdf}
  }
    \hspace{-2em}
  \subfigure[Incomplete Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{}
  \label{fig:vs-n}
\end{figure*}
